\documentclass[12pt,a4paper]{report}

% ------------------------------------------------
% Packages
% ------------------------------------------------
\usepackage[utf8]{inputenc}       % Encoding
\usepackage{amsmath, amssymb}     % Math symbols
\usepackage{graphicx}             % Figures
\usepackage{hyperref}             % Clickable refs
\usepackage{natbib}               % References
\usepackage{setspace}             % Line spacing
\usepackage{geometry}             % Page layout
\usepackage{listings}             % Code listings
\usepackage{caption}              % Better captions

% Page layout
\geometry{margin=1in}
\doublespacing

% ------------------------------------------------
% Metadata
% ------------------------------------------------
\title{Convergence and Stability in Deep Reinforcement Learning}
\author{Sam Nguyen}
\date{Honours Thesis \\ University of Sydney \\ 2025}

% ------------------------------------------------
% Document
% ------------------------------------------------
\begin{document}

% Title page
\maketitle

% Abstract
\begin{abstract}
This thesis investigates the convergence and stability properties of reinforcement learning (RL) algorithms, with a focus on deep policy-gradient and value-based methods. We provide theoretical analysis supported by empirical validation on benchmark environments.
\end{abstract}

% Acknowledgements
\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
I would like to thank my supervisors, colleagues, and family for their support.

% Table of contents
\tableofcontents
\listoffigures
\listoftables

% ------------------------------------------------
% Chapters
% ------------------------------------------------

\chapter{Introduction}
- What is reinforcement learning?  
- Why study convergence and stability?  
- Research gap and contributions.  

\chapter{Background}
- RL foundations: MDPs, policies, value functions.  
- The “deadly triad” (function approximation, bootstrapping, off-policy).  
- Related work on convergence guarantees.  

\chapter{Methodology}
- Theoretical analysis of policy gradient methods.  
- Error propagation in value-based methods.  
- Experimental setup (environments, baselines, metrics).  

\chapter{Experiments}
- Describe environments (CartPole, Atari, MuJoCo, etc.).  
- Present results with figures and tables.  
- Compare stability across runs.  

\chapter{Discussion}
- Interpret results in light of theory.  
- Limitations of experiments.  
- Implications for future RL research.  

\chapter{Conclusion}
- Summary of contributions.  
- Open questions and directions.  

% ------------------------------------------------
% References
% ------------------------------------------------
\bibliographystyle{plainnat}
\bibliography{references}

% ------------------------------------------------
% Appendices
% ------------------------------------------------
\appendix
\chapter{Additional Proofs}
\chapter{Experiment Details}

\end{document}
